Diagnostic Plots

### 2024-08-12 pre_print_manuscript.qmd
Revised results section complete - adding study simulations and also pub bias/QRP models.

To begin with we examined through simulation what impact a single new trial might have had upon shifting belief in the prior estimate yielded by the meta-analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. Sample size was simulated as 10, 20, 40, 80, 160, 320, 640, 1282, 2560, and 5120[^6] with a 50:50 allocation to either self-talk intervention or control conditions, and we varied the sample effect size as an SMD of 0, 0.2, 0.4, 0.6, 0.8, and 1.0 reflecting a range from no effect of self-talk interventions to a large  effect. In each combination of sample size and true effect size we set the sample parameters to  the SMD and its corresponding sampling variance was calculated and then included as a single observation in a Bayesian random effects meta-analysis where the priors was set informatively for the intervention effects, and were set to be default weakly regularising for the heterogeneity (i.e., $\tau$)[^7]. Intervention effects were set with priors based on the effect estimates from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], reported in their Table 1, using a $t$-distribution ($t(k,\mu,\sigma)$) with $k-2$ degrees of freedom [@higginsReevaluationRandomeffectsMetaanalysis2009]. We assumed $k$ to be the number of effects included in the models reported by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. The prior for the intervention effect was set directly on the model intercept i.e., $t(60, 0.48, 0.05)$. The prior for heterogeneity was set as the default weakly regularising prior in `brms`; a half-$t$-distribution with $\mu=0$, $\sigma=2.5$, and $k=3$. This constrained the prior to only allow positively signed values for $\tau$ though over a wide range of possible values. We fit each model using four Monte Carlo Markov Chains each with 2000 warmup and 6000 sampling iterations.

@@

In addition to this we also examined both the mixture model for *p*-hacking [@mossModellingPublicationBias2023] and RoBMA [@@bartosRobustBayesianMetaanalysis2023] (both with, and without, the inclusion of an informative prior on the intervention effect from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]) though ignored the hierarchical structure to the data. The mixture model for for *p*-hacking provides an adjusted estimate of the intervention effect under the assumption that *p*-hacking such as excluding observations, collecting new data *ex-post*, or selectively including covariates has occured to produce the effects we see in the literature. The RoBMA fits a total of 36 different models with varying assumptions regarding the true data generating process underlying the included studies/effects and thus reflecting our uncertainty in it: selection models varying sidedness of the tests (one- or two-sided) and the specific *p*-value cutoffs used (combinations of 0.025, 0.05, 0.10, and 0.50), the PET-PEESE regression based models, assuming there is/is not an intervention effect, assuming there is/is not heterogeneity, and assuming there is/is not publication bias. These models are then combined using Bayesian model-averaging and weighted based on how well the model fit the data. Bayes Factors were then calculated to examine the evidence in favour of there being an effect, the presence of heterogeneity, and publication bias.

# Results
```{r}
targets::tar_load(data)
sample_sizes_st <- data %>%
  select(group, n_st) %>%
  group_by(group) %>%
  summarise(n_st = max(n_st)) %>%
  summarise(`All ST` = sum(n_st),
            `Minumum ST` = min(n_st),
            `Median ST` = median(n_st),
            `Maximum ST` = max(n_st)
            ) %>%
  pivot_longer(1:4, names_to = "Group", values_to = "Sample Size")
sample_sizes_con <- data %>%
  select(study, n_con) %>%
  group_by(study) %>%
  summarise(n_con = max(n_con)) %>%
  summarise(`All CON` = sum(n_con, na.rm =TRUE), 
            `Minumum CON` = min(n_con, na.rm =TRUE),
            `Median CON` = median(n_con, na.rm =TRUE),
            `Maximum CON` = max(n_con, na.rm =TRUE)) %>%
  pivot_longer(1:4, names_to = "Group", values_to = "Sample Size")
sample_sizes <- bind_rows(sample_sizes_st, sample_sizes_con)

@@

We identified `r length(unique(data$study))` new studies published from November 2011 up to November 2023 [@abdoliCloserLookHow2018; @hatzigeorgiadisSelftalkCompetitiveSport2014; @panteliAcquisitionLongJump2013; @hongEmpiricalTestSelfTalk2020; @hatzigeorgiadisBeatHeatEffects2018; @laneBriefOnlineTraining2016; @latinjakCombiningSelfTalk2011; @gregersenCounteringConsequencesEgo2017; @mccormickEffectsMotivationalSelfTalk2018; @galanisEffectsStrategicSelftalk2022; @benekaEffectsInstructionalMotivational2013; @wallaceEffectsMotivationalSelfTalk2017; @walterEffectsSelfTalkTraining2019; @galanisLabFieldEffects2018; @youngHowMuchDoes2023; @raalteWillUseDeclarative2018; @liuInteractiveEffectsMotor2022; @dematosMotivationalSelftalkImproves2021; @barwoodImprovement10kmTimetrial2015; @cabralMotivationalSelftalkMitigates2023; @changSelftalkSoftballPerformance2014; @raalteSelfTalkSCUBADiving2018; @galanisStrategicSelfTalkAssists2022; @blanchfieldTalkingYourselfOut2014; @turnerTeeingSuccessEffects2018; @naderiradEffectInstructionalMotivational2023; @zetouEffectSelftalkTaekwondo2014; @zourbanosEffectsSelftalkIntervention2013; @osmanEffectsInstructionalMotivational2022; @kolovelonisEffectsInstructionalMotivational2011; @sarigEffectsInstructionalSelfTalk2023; @marshallEffectsSelfTalkCues2016; @zourbanosEffectsSelfTalkDominant2013; @galanisEffectsStrategicSelftalk2023; @weinbergInfluenceSelftalkIntervention2012]. These included `r length(unique(data$effect))` effects nested in `r length(unique(data$group))` groups nested in `r length(unique(data$experiment))` experiments. The included studies contained a total of `r sample_sizes[1,2] + sample_sizes[5,2]` participants (see @tbl-sample-sizes). We included all but one study [@marshallEffectsSelfTalkCues2016], due to the sample size for groups in this study being too small to calculate SMDs (i.e., n = 2 to 3), in our analyses.

@@

## Examining the effects of a new trial upon belief in the effects of self-talk interventions

@@

Considering the log10(BF) values calculated against the range of SMD effect sizes from 0 to 1 compared to Jeffreys scale (see @fig-main-model panel [C]), the newly added evidence suggested that there was only "Decisive" evidence updating the prior against effect sizes ranging from 0 to `r round(Jeffreys_scales$max_effect[1],2)` and from `r round(Jeffreys_scales$min_effect[2],2)` to `r round(Jeffreys_scales$max_effect[2],2)`. "Very Strong" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[7],2)` to `r round(Jeffreys_scales$max_effect[7],2)` and from `r round(Jeffreys_scales$min_effect[8],2)` to `r round(Jeffreys_scales$max_effect[8],2)`. "Strong" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[3],2)` to `r round(Jeffreys_scales$max_effect[3],2)` and from `r round(Jeffreys_scales$min_effect[4],2)` to `r round(Jeffreys_scales$max_effect[4],2)`. "Substantial" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[5],2)` to `r round(Jeffreys_scales$max_effect[5],2)` and from `r round(Jeffreys_scales$min_effect[6],2)` to `r round(Jeffreys_scales$max_effect[6],2)`. "Weak" or "Negative" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[9],2)` to `r round(Jeffreys_scales$max_effect[10],2)`. This suggested that the newly acquired evidence generally decreased our belief in effect sizes that would likely already have been ruled out by the analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. The supplementary cumulative models further supported this. They showed little change in either point or interval estimates for the SMD from year to year as a result of new studies during the period of November 2011 to November 2023 (see [https://osf.io/9qrh5](cumulative model plot)).

@@

For most of the moderators explored there was similarly little impact upon posterior estimates for the SMD from the introduction of new evidence accumulated since the analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. @fig-moderators-models shows each of the prior and posterior distributions for the moderators estimates and the log10(BF) results for each are available in the supplementary materials (see 'plots' folder [https://osf.io/dqwh5/](https://osf.io/dqwh5/)). Where there were more substantial changes from prior to posterior these typically revealed a reduction in the magnitude of SMD estimate e.g., for fine tasks in the motor demands model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.67 [95% confidence interval: 0.53, 0.82]; posterior pooled estimate = `r round(tidy_motor_demands_model$estimate[1],2)` [95% quantile interval: `r round(tidy_motor_demands_model$conf.low[1],2)`, `r round(tidy_motor_demands_model$conf.high[1],2)`]), instructional in the self-talk content model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.55 [95% confidence interval: 0.40, 0.70]; posterior pooled estimate = `r round(tidy_selftalk_content_model$estimate[2],2)` [95% quantile interval: `r round(tidy_selftalk_content_model$conf.low[2],2)`, `r round(tidy_selftalk_content_model$conf.high[2],2)`]), instructional/fine in the matching hypothesis model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.83 [95% confidence interval: 0.64, 1.02]; posterior pooled estimate = `r round(tidy_matching_model$estimate[1],2)` [95% quantile interval: `r round(tidy_matching_model$conf.low[1],2)`, `r round(tidy_matching_model$conf.high[1],2)`]), for novel tasks in the task novelty model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.73 [95% confidence interval: 0.47, 1.00]; posterior pooled estimate = `r round(tidy_task_novelty_model$estimate[2],2)` [95% quantile interval: `r round(tidy_task_novelty_model$conf.low[2],2)`, `r round(tidy_task_novelty_model$conf.high[2],2)`]), and for training interventions in the training model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.80 [95% confidence interval: 0.57, 1.03]; posterior pooled estimate = `r round(tidy_training_model$estimate[2],2)` [95% quantile interval: `r round(tidy_training_model$conf.low[2],2)`, `r round(tidy_training_model$conf.high[2],2)`]).

@@

## Examining the quality of the evidence and potential questionable research practices

>>>>

### Examining the effects of a new trial upon belief in the effects of self-talk interventions
To begin with we examined through simulation what impact a single new trial might have had upon shifting belief in the prior estimate yielded by the meta-analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. Sample size was simulated as 10, 20, 40, 80, 160, 320, 640, 1282, 2560, and 5120[^6] with a 50:50 allocation to either self-talk intervention or control conditions, and we varied the sample effect size as an SMD of 0, 0.2, 0.4, 0.6, 0.8, and 1.0 reflecting a range from no effect of self-talk interventions to a large  effect. In each combination of sample size and true effect size we set the sample parameters to the SMD and its corresponding sampling variance was calculated and then included as a single observation in a Bayesian random effects meta-analysis where the priors was set informatively for the intervention effects, and were set to be default weakly regularising for the heterogeneity (i.e., $\tau$)[^7]. Intervention effects were set with priors based on the effect estimates from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], reported in their Table 1, using a $t$-distribution ($t(k,\mu,\sigma)$) with $k-2$ degrees of freedom [@higginsReevaluationRandomeffectsMetaanalysis2009]. We assumed $k$ to be the number of effects included in the models reported by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. The prior for the intervention effect was set directly on the model intercept i.e., $t(60, 0.48, 0.05)$. The prior for heterogeneity was set as the default weakly regularising prior in `brms`; a half-$t$-distribution with $\mu=0$, $\sigma=2.5$, and $k=3$. This constrained the prior to only allow positively signed values for $\tau$ though over a wide range of possible values. We fit each model using four Monte Carlo Markov Chains each with 2000 warmup and 6000 sampling iterations.

@@

In addition to this we also examined both the random effects mixture model for *p*-hacking [@mossModellingPublicationBias2023] and RoBMA [@@bartosRobustBayesianMetaanalysis2023] (both with, and without, the inclusion of an informative prior[^9] on the intervention effect from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], yet with default priors for all other parameters) though ignored the hierarchical structure to the data as these models respectively have not been extended to the multilevel case or are too computationally intractable at present. The random effects mixture model for for *p*-hacking provides an adjusted estimate of the intervention effect under the assumption that questionable research practices such as excluding observations, collecting new data *ex-post*, or selectively including covariates has occurred to produce a one-sided $\alpha\leq0.05$ (to reflect the fact that typically it is effects in a particular direction that are of interest) or $\alpha\leq0.025$ to account for reporting of two-sided tests. The adjusted estimate assuming the presence of *p*-hacking was then compared to a classical random effects model estimate. Both the *p*-hacking and classical models were fit using Bayesian estimation. The RoBMA fits a total of 36 different models with varying assumptions regarding the true data generating process underlying the included studies/effects and thus reflecting our uncertainty in it: selection models for publication varying sidedness of the tests (one- or two-sided) and the specific *p*-value cutoffs used (combinations of 0.025, 0.05, 0.10, and 0.50), the PET-PEESE regression based models, models assuming there is/is not an intervention effect, models assuming there is/is not heterogeneity, and models assuming there is/is not publication bias. These models are then combined using Bayesian model-averaging and weighted based on how well the model fit the data. Bayes Factors were then calculated to examine the evidence in favour of there being an effect, the presence of heterogeneity, and publication bias.

[^9]: Note that for the mixture model of *p*-hacking the `publipha` package used does not allow for specification of a prior based upon the $t$ distribution for that function. As such, instead of the $t(60, 0.48, 0.05)$ prior taken from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] for these models we used a normal prior with the same location and scale parameters. Given the the $t$ distribution approaches the normal distribution with high degrees of freedom, and the prior for other models had a high number of degrees of freedom (i.e., $k=60$), the choice of a normal distribution here very closely approximates the $t$ distribution based prior anyway.

# Results
```{r}
targets::tar_load(data)
sample_sizes_st <- data %>%
  select(group_code, n_st) %>%
  group_by(group_code) %>%
  summarise(n_st = max(n_st)) %>%
  summarise(`All ST` = sum(n_st),
            `Minumum ST` = min(n_st),
            `Median ST` = median(n_st),
            `Maximum ST` = max(n_st)
            ) %>%
  pivot_longer(1:4, names_to = "Group", values_to = "Sample Size")
sample_sizes_con <- data %>%
  select(study_code, n_con) %>%
  group_by(study_code) %>%
  summarise(n_con = max(n_con)) %>%
  summarise(`All CON` = sum(n_con, na.rm =TRUE), 
            `Minumum CON` = min(n_con, na.rm =TRUE),
            `Median CON` = median(n_con, na.rm =TRUE),
            `Maximum CON` = max(n_con, na.rm =TRUE)) %>%
  pivot_longer(1:4, names_to = "Group", values_to = "Sample Size")
sample_sizes <- bind_rows(sample_sizes_st, sample_sizes_con)

@@

Since Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] meta-analysis the number of studies conducted examining the effects of self-talk interventions on sport/motor performance has roughly doubled. We identified `r length(unique(data$study_code))` new studies published from November 2011 up to November 2023 [@abdoliCloserLookHow2018; @hatzigeorgiadisSelftalkCompetitiveSport2014; @panteliAcquisitionLongJump2013; @hongEmpiricalTestSelfTalk2020; @hatzigeorgiadisBeatHeatEffects2018; @laneBriefOnlineTraining2016; @latinjakCombiningSelfTalk2011; @gregersenCounteringConsequencesEgo2017; @mccormickEffectsMotivationalSelfTalk2018; @galanisEffectsStrategicSelftalk2022; @benekaEffectsInstructionalMotivational2013; @wallaceEffectsMotivationalSelfTalk2017; @walterEffectsSelfTalkTraining2019; @galanisLabFieldEffects2018; @youngHowMuchDoes2023; @raalteWillUseDeclarative2018; @liuInteractiveEffectsMotor2022; @dematosMotivationalSelftalkImproves2021; @barwoodImprovement10kmTimetrial2015; @cabralMotivationalSelftalkMitigates2023; @changSelftalkSoftballPerformance2014; @raalteSelfTalkSCUBADiving2018; @galanisStrategicSelfTalkAssists2022; @blanchfieldTalkingYourselfOut2014; @turnerTeeingSuccessEffects2018; @naderiradEffectInstructionalMotivational2023; @zetouEffectSelftalkTaekwondo2014; @zourbanosEffectsSelftalkIntervention2013; @osmanEffectsInstructionalMotivational2022; @kolovelonisEffectsInstructionalMotivational2011; @sarigEffectsInstructionalSelfTalk2023; @marshallEffectsSelfTalkCues2016; @zourbanosEffectsSelfTalkDominant2013; @galanisEffectsStrategicSelftalk2023; @weinbergInfluenceSelftalkIntervention2012]. These included `r length(unique(data$effect_code))` effects nested in `r length(unique(data$group_code))` groups nested in `r length(unique(data$experiment_code))` experiments. The included studies contained a total of `r sample_sizes[1,2] + sample_sizes[5,2]` participants (see @tbl-sample-sizes). We included all but one study [@marshallEffectsSelfTalkCues2016], due to the sample size for groups in this study being too small to calculate SMDs (i.e., n = 2 to 3), in our analyses.

@@

## Examining the effects of a new trial upon belief in the effects of self-talk interventions
```{r}
#| label: fig-additional-study 
#| fig-width: 13.33
#| fig-height: 7.5
#| fig-cap: Prior and posterior distributions after the addition of a single new study yielding a single new effect varying in magnitude of standardised mean difference (null through to SMD=1 favouring self-talk interventions) and varying sample size of the new study (from n=10 to 5120).
targets::tar_load(additional_study_sims_plot)

additional_study_sims_plot
```
Given the precision of the prior distribution taken from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] it is highly unlikely that any further study would have shifted belief in the effect estimate. As can be seen in @fig-additional-study, irrespective of the sample size or magnitude of effect and the extent to which it disagreed with the prior estimate, no single new study could shift the posterior distribution to an extent that it didn't still have ~95% of its mass within the 95% quantile interval of the prior distribution. As such, if we were to take the prior estimate from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] at face value in the process of deciding whether to conduct a new study of self-talk interventions, at least with respect to their main effects on sport/motor performance, we should likely conclude that it would be a waste of resources given the precision of this existing estimate of the intervention effect. Of course, this only considers the addition of a single study and as noted since 2011 the number of studies examining self-talk interventions has roughly doubled. As such, it is worth considering the extent to which this volume of additional evidence might have updated belief in the estimate of their effects.

@@

Considering the log10(BF) values calculated against the range of SMD effect sizes from 0 to 1 compared to Jeffreys scale (see @fig-main-model panel [C]), the newly added evidence suggested that there was only "Decisive" evidence updating the prior against effect sizes ranging from 0 to `r round(Jeffreys_scales$max_effect[1],2)` and from `r round(Jeffreys_scales$min_effect[2],2)` to `r round(Jeffreys_scales$max_effect[2],2)`. "Very Strong" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[7],2)` to `r round(Jeffreys_scales$max_effect[7],2)` and from `r round(Jeffreys_scales$min_effect[8],2)` to `r round(Jeffreys_scales$max_effect[8],2)`. "Strong" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[3],2)` to `r round(Jeffreys_scales$max_effect[3],2)` and from `r round(Jeffreys_scales$min_effect[4],2)` to `r round(Jeffreys_scales$max_effect[4],2)`. "Substantial" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[5],2)` to `r round(Jeffreys_scales$max_effect[5],2)` and from `r round(Jeffreys_scales$min_effect[6],2)` to `r round(Jeffreys_scales$max_effect[6],2)`. "Weak" or "Negative" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[9],2)` to `r round(Jeffreys_scales$max_effect[10],2)`. This suggested that the newly acquired evidence generally decreased our belief only in effect sizes that would likely already have been ruled out by the analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. The supplementary cumulative models further supported this. They showed little change in either point or interval estimates for the SMD from year to year as a result of new studies during the period of November 2011 to November 2023 (see [https://osf.io/9qrh5](cumulative model plot)).

@@

For most of the moderators explored there was similarly little impact upon posterior estimates for the SMD from the introduction of new evidence accumulated since the analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. @fig-moderators-models shows each of the prior and posterior distributions for the moderators estimates and the log10(BF) results for each are available in the supplementary materials (see 'plots' folder [https://osf.io/dqwh5/](https://osf.io/dqwh5/)). Where there were more substantial changes from prior to posterior these typically revealed a shift in the magnitude of SMD estimate towards the overall pooled estimate from the main model e.g., for fine tasks in the motor demands model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.67 [95% confidence interval: 0.53, 0.82]; posterior pooled estimate = `r round(tidy_motor_demands_model$estimate[1],2)` [95% quantile interval: `r round(tidy_motor_demands_model$conf.low[1],2)`, `r round(tidy_motor_demands_model$conf.high[1],2)`]), instructional in the self-talk content model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.55 [95% confidence interval: 0.40, 0.70]; posterior pooled estimate = `r round(tidy_selftalk_content_model$estimate[2],2)` [95% quantile interval: `r round(tidy_selftalk_content_model$conf.low[2],2)`, `r round(tidy_selftalk_content_model$conf.high[2],2)`]), instructional/fine in the matching hypothesis model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.83 [95% confidence interval: 0.64, 1.02]; posterior pooled estimate = `r round(tidy_matching_model$estimate[1],2)` [95% quantile interval: `r round(tidy_matching_model$conf.low[1],2)`, `r round(tidy_matching_model$conf.high[1],2)`]), for novel tasks in the task novelty model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.73 [95% confidence interval: 0.47, 1.00]; posterior pooled estimate = `r round(tidy_task_novelty_model$estimate[2],2)` [95% quantile interval: `r round(tidy_task_novelty_model$conf.low[2],2)`, `r round(tidy_task_novelty_model$conf.high[2],2)`]), and for training interventions in the training model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.80 [95% confidence interval: 0.57, 1.03]; posterior pooled estimate = `r round(tidy_training_model$estimate[2],2)` [95% quantile interval: `r round(tidy_training_model$conf.low[2],2)`, `r round(tidy_training_model$conf.high[2],2)`]).

@@

## Examining the quality of the evidence and potential questionable research practices
```{r}
targets::tar_load(tidy_pet_model)
targets::tar_load(tidy_rma.mv_model)
targets::tar_load(null_robma_model)
targets::tar_load(prior_robma_model)
targets::tar_load(tidy_p_hack_model)
targets::tar_load(tidy_classic_model)
targets::tar_load(tidy_p_hack_model_prior)
targets::tar_load(tidy_classic_model_prior)

targets::tar_load(p_hack_models_plots)

```{r}
#| label: fig-contour-plot 
#| fig-width: 5
#| fig-height: 5
#| fig-cap: Countour enhanced funnel plot showing effect sizes (scaled in size by inverse sampling variance), thresholds for *p* < 0.05 and 0.01, and both PET-PEESE estimate (in this case it is the PET estimate from the conditional estimator; regression line and ribbon plus "Multilevel PET Estimate" labelled point and interval) and frequentist multilevel model estimate ("Main Model Estimate" labelled point and interval).
targets::tar_load(main_model_contour_funnel_plot)

main_model_contour_funnel_plot

When considering only the new studies published since Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] the frequentist multilevel model estimate (`r round(tidy_rma.mv_model$estimate[1],2)` [95% confidence interval: `r round(tidy_rma.mv_model$conf.low[1],2)`, `r round(tidy_rma.mv_model$conf.high[1],2)`]) was very similar to both their prior estimate, and also the posterior Bayesian estimate from our updated model (see section above). For the conditional PET-PEESE estimator however the PET estimate was not statistically significant at the $\alpha=0.10$ level and this adjusted estimate was compatible with a range of estimates from negative effects of similar magnitude to the previosly reported positive effect in Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], through to null and trivial positive(`r round(tidy_pet_model$estimate[1],2)` [95% confidence interval: `r round(tidy_pet_model$conf.low[1],2)`, `r round(tidy_pet_model$conf.high[1],2)`]) suggesting that publication bias/small study effects may be present in this literature. These estimates can be seen in the contour enhanced funnel plot in @fig-contour-plot.

```{r}
#| label: fig-phack-plot 
#| fig-width: 5
#| fig-height: 5
#| fig-cap: Countour enhanced funnel plot showing effect sizes (scaled in size by inverse sampling variance), thresholds for *p* < 0.05 and 0.01, and both PET-PEESE estimate (in this case it is the PET estimate from the conditional estimator; regression line and ribbon plus "Multilevel PET Estimate" labelled point and interval) and frequentist multilevel model estimate ("Main Model Estimate" labelled point and interval).
targets::tar_load(main_model_contour_funnel_plot)

main_model_contour_funnel_plot

```
The Bayesian mixture models assuming the presence of *p*-hacking (note, recall these models ignore the multilevel structure of the effects) also provided reduced adjusted effect estimates, though not to the same magnitude as seen in the PET estimate, with this reduction more prominent when only considering the post-2011 studies and not incorporating the prior from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. Without the prior the estimate from a classic random effects model was `r round(tidy_classic_model$estimate[1],2)` [95% quantile interval: `r round(tidy_classic_model$conf.low[1],2)`, `r round(tidy_classic_model$conf.high[1],2)`] and was reduced to `r round(tidy_p_hack_model$estimate[1],2)` [95% quantile interval: `r round(tidy_p_hack_model$conf.low[1],2)`, `r round(tidy_p_hack_model$conf.high[1],2)`] assuming the presence of *p*-hacking. When incorporating the prior from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] the estimate from a classic random effects model was `r round(tidy_classic_model_prior$estimate[1],2)` [95% quantile interval: `r round(tidy_classic_model_prior$conf.low[1],2)`, `r round(tidy_classic_model_prior$conf.high[1],2)`] and was reduced to `r round(tidy_p_hack_model_prior$estimate[1],2)` [95% quantile interval: `r round(tidy_p_hack_model_prior$conf.low[1],2)`, `r round(tidy_p_hack_model_prior$conf.high[1],2)`] assuming the presence of *p*-hacking. These estimates and the posterior distributions can be seen in @fig-phack-plot.

When considering only the post-2011 studies and utilising default prior distributions, robust Bayesian meta-analysis found strong evidence against the effect, $BF_{10}=$`r round(summary(null_robma_model)$components$inclusion_BF[1],3)` with mean model-averaged estimate of `r round(summary(null_robma_model)$estimates$Mean[1],2)` [95% quantile interval: `r round(summary(null_robma_model)$estimates[1,3],2)`, `r round(summary(null_robma_model)$estimates[1,3],2)`, strong evidence in favor of the heterogeneity, $BF_{rf}$ = `r round(summary(null_robma_model)$components$inclusion_BF[2],3)` with mean model-averaged estimate $\tau=$`r round(summary(null_robma_model)$estimates$Mean[2],2)` [95% quantile interval: `r round(summary(null_robma_model)$estimates[2,3],2)`, `r round(summary(null_robma_model)$estimates[2,3],2)`. Robust Bayesian meta-analysis found strong evidence in favor of the publication bias, BF_pb = `r round(summary(null_robma_model)$components$inclusion_BF[3],3)`. When including the prior from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] results were similar with robust Bayesian meta-analysis finding strong evidence against the effect, $BF_{10}=$`r round(summary(prior_robma_model)$components$inclusion_BF[1],3)` with mean model-averaged estimate of `r round(summary(prior_robma_model)$estimates$Mean[1],2)` [95% quantile interval: `r round(summary(prior_robma_model)$estimates[1,3],2)`, `r round(summary(prior_robma_model)$estimates[1,3],2)`, strong evidence in favor of the heterogeneity, $BF_{rf}$ = `r round(summary(prior_robma_model)$components$inclusion_BF[2],3)` with mean model-averaged estimate $\tau=$`r round(summary(prior_robma_model)$estimates$Mean[2],2)` [95% quantile interval: `r round(summary(prior_robma_model)$estimates[2,3],2)`, `r round(summary(prior_robma_model)$estimates[2,3],2)`. Robust Bayesian meta-analysis found strong evidence in favor of the publication bias, BF_pb = `r round(summary(prior_robma_model)$components$inclusion_BF[3],3)`.
